The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190922.tex
CIV tex/ tidy up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
%\subsection{Selection/Identification}
\subsection{Spectra}
An overview of our spectroscopic observations is given in Table~\ref{tab:obs_notes}. 
The spectra are from the SDSS \citep{Stoughton2002, DR7, Schneider2010},  
the SDSS-III Baryon Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011, Dawson2013, Smee2013, Alam2015, Paris2017} 
and the SDSS-IV  Extended Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016, Abolfathi2018}. 
These quasars were targetted via a range of techniques and algorithms \citep[][]{Richards2002, Ross2012, 
Myers2015}.  
These data are supplemented by spectra from 
the Low Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I} telescope \citep{Oke1995}. 
%% The Keck Low Resolution Imaging Spectrometer", Oke, J.B., et al.. 1995, PASP, 107, 375
and the Double Spectrograph (DBSP) instrument on the Palomar {\it Hale} 5m telescope.

\subsection{Line Properties}. 
We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}. \citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.} The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS. These measurements provide line profile information and N V/C IV flux ratios...

\begin{table}
 \centering
 \begin{tabular}{l l l l}
  \hline \hline 
% &&\\
   Quantity \ Object                           & J2228+2201     &  J1638+2827 \\
% &&\\
 \hline 
    &&\\
    R.A. / deg                                        &    337.078194      &  249.720559\\
    Declination / deg                            &    +22.017478      &  +28.452159 \\
    redshift, $z$                                    &   2.222$\pm$0.00038   &  2.185$\pm$0.00043          \\
    &&\\ 
    \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
                                         & 7582, 790, 56960	     & 5201, 178, 55832 \\    
 %   &&\\ 
    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
    &&\\
    \hline \hline 
  \end{tabular}
  \caption{Physical properties of J1100-0053, J2317+0005 and J1052+1519 using the
    methods from \citet{Shen2011}. *This spectrum was used to estimate
    the quantities reported.  We use the regular definition of $L_{\rm
      Edd} = 4 \pi G M m_{\rm p} c /\sigma_{T} =
    1.26\times10^{38}\left (M/M_{\odot} \right )$ erg s$^{-1}$.} 
 \label{tab:Shen_props}
\end{table}

\begin{table*}
 \centering
 \begin{tabular}{r  r  r r r   r r r r}
  \hline \hline 
% &&\\
   Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{Mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}   & Exposure    & \multirow{3}{*}{Spectrum} & \multirow{3}{*}{Notes} \\
   R.A. / deg                   &               &               &            &                                &                                                                       &  Time         & & \\
   Decl. / deg                 &               &               &            &                                &                                                                       &  / seconds         & & \\

% &&\\
 \hline 
                                       &                &               &            &                              &                   &                             &  & \\
   J120544.7+342252.4   & 2.071     &   17.99   & 53498 & 2005-May-08   & SDSS             & ?                          & 53498-2089-427  & \\
          181.436164           &                &               & 58538 & 2019-Feb-24     & DBSP            &  2$\times$900    &                               &  Conditions? \\
         +34.381229           &                &               & 58693 & 2019-Jul-29      & DBSP            &  2$\times$1200   &                                &   \\
                                       &                &               &              &                           &                   &                             &  & \\
   J163852.9+282707.7   & 2.182     &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
      249.720558407	       &               &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
       +28.452158884        &               &              & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
                                       &                &               &              &                           &                   &                             &  & \\
    J222818.7+220102.9   & 2.222     & 19.97    & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
        337.078194              &              &              & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
        +22.017478                                &               &             & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
                                       &                &               &            &                             &                   &                              &  & \\
%   J232446.7+140029.5   &  0.916     &  18.83   &  56209 & 2012-Oct-09   & BOSS             & ?                             & 56209-6148-743   & \\
 %                                      &                &               &   58662 & 2019-Jun-28  &   (??)DBSP       & ?                            &  & \\
  %                                     &                &               &              &                           &                   &                              &  & \\
   \hline \hline   
  \end{tabular}
  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
Exposure times are from the {\tt plate.fits} file. 
DBSP on the Palomar 200-inch telescope is the } 
 \label{tab:obs_notes}
\end{table*}

\subsection{Multi-wavelength properties}
MIR \\
Radio \\
{\bf FROM ROSS ET AL 2018!!!!} 
While previous efforts have used the 1-year baseline of the WISE mission to identify
changing-look quasars \citep[e.g.,][]{Assef2018, Stern2018}, our
investigation is the first to extend this selection to the infrared
using NEOWISE-R mission data. We have identified a sample of Sloan
Digital Sky Survey (SDSS) quasars that show significant changes in
their IR flux over the course of a few years. Importantly, our IR
light curves enable us to set limits on SED changes due to
obscuration.

We use data from the
beginning of the WISE mission \citep[2010 January; ][]{Wright2010}
through the thrid-year of NEOWISE-R operations \citep[2016 December;
][]{Mainzer2011}. The WISE scan pattern leads to coverage of the
full-sky approximately once every six months (a ``sky pass''), but the
satellite was placed in hibernation in 2011 February and then
reactivated in 2013 October. Hence, our light curves have a cadence of
6 months with a 32 month sampling gap.

The W1/W2 light curves for $\sim$200,000 SDSS and BOSS spectroscopic
quasars were obtained by performing forced photometry at the locations
of DECam-detected optical sources \citep{Lang2014, Meisner2017a,
Meisner2017b}. This forced photometry was performed on time-resolved
coadds \citep{Lang2014}, each of which represents a stack of $\sim$12
exposures. The coaddition removes the possibility of probing
variability on $\lesssim$1 day time scales, but pushes $\approx$1.4
magnitudes deeper than individual exposures while removing virtually
all single-exposure artifacts (e.g. cosmic rays and satellites).

Approximately $\sim$30,000 of the SDSS/BOSS quasars with W1/W2
light-curves available are `IR-bright', in that they are above both
the W1 and W2 single exposure thresholds and therefore detected at
very high significance in the coadds. For this ensemble of objects,
the typical variation in each quasar's measured (W1-W2) color is 0.06
magnitudes.  This includes statistical and systematic errors which are
expected to contribute variations at the few hundredths of a magnitude
level. The typical measured single-band scatter is 0.07 magnitudes in
each of W1 and W2.

%%\newpage
%% For the MNRAS Letter, not sure this can take up a full page...
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
% {figures/The_3_CIV_CLQs_20190917.pdf}
   \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
SDSS J1205+3422 (top), 
SDSS J1638+2827 (middle), 
SDSS J2228+2201 (bottom). 
%A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
}
  \label{fig:civ_clqs}
\end{figure}

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  % {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
  {../plots/perObject/J1205+3422_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  {../plots/perObject/J1638+2827_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  {../plots/perObject/J2228+2201_landscape_20190920.png}
  \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
    SDSS J1205+3422 (top), 
    SDSS J1638+2827 (middle), 
    SDSS J2228+2201 (bottom). 
    % A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
  }
  \label{fig:civ_clqs2}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
%%
%%
For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
standard UV/blue continuum slope increases in flux. 
the UV/blue continuum diminishes and the shape of \lya changes.

@@

In the context of CLQs at lower-$z$...  Sociis natoque penatibus et
magnis dis parturient montes, nascetur ridiculus mus. Duis tempus,
lectus nec ultricies mollis, mi orci feugiat nulla, a bibendum velit
orci nec lacus. Duis a odio in nisi egestas dictum. Nullam vel quam
mauris, eget consectetur orci. Morbi ac mi sit amet neque consectetur
tempus ac eget est. Curabitur malesuada arcu sit amet metus dictum at
dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.  Balmer CLQs
vs. \civ CLQs...

\subsection{J1205+3422 }
SDSS J120544.67+342252.4, observed by SDSS, first reported in \citet{Schneider2007}. 
Redshift of $z=$2.068$\pm$0.00027. 
%% targeting_flags	SERENDIP_BLUE QSO_CAP
plate	2089 
mjd	53498
fiberid	427

\subsection{J1638+2827}
SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
First reported in \citet{Schneider2010}. 
Selected by {\tt SERENDIP\_BLUE} and {\tt QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.

R.A. (J2000) = 249.72058 degs. \\
Decl. (J2000) = 28.45217 degs. \\
\href{skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232}{SDSS SkyServer} 
All Spectra of this Object:: \\
specObjId	plate	MJD	fiber	ra	dec	redshift \\
5855854441601671168	5201	55832	178	2.186$\pm$0.00073\\
3319321776793610240	2948	54553	614	2.185$\pm$0.00043\\

\subsection{J2228+2201}
SDSS J222818.76+220102.9 (R.A. 337.078194926, Decl. 22.017477924) was first reported in 
\citet{Paris2017}.

%%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
\href{skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655}{SDSS SkyServer}
All Spectra of this Object:: \\
specObjId	plate	MJD	fiber	ra	dec	redshift \\
8536790363997708288	7582	56960	790	2.222$\pm$0.00038\\
6888453645991387136	6118	56189	720	2.217$\pm$0.00208\\

%Plate: 2948, MJD: 54553, Fiber: 0614
%https://dr12.sdss.org/spectrumDetail?mjd=54553&fiber=614&plateid=2948

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
%%\subsection{Selection/Identification}
{\bf MJG to write a few notes on how the CIV CLQs were identified....}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam
porta sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.

\begin{table*}
 \centering
 \begin{tabular}{r  r  r r r   r r r r}
  \hline \hline 
% &&\\
   Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{$dg$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}   & Exposure    & \multirow{3}{*}{Spectrum} & \multirow{3}{*}{Notes} \\
   R.A. / deg                   &               &               &            &                                &                                                                       &  Time         & & \\
   Decl. / deg                 &               &               &            &                                &                                                                       &  / seconds         & & \\

% &&\\
 \hline 
                                       &                                   &                        &             &                          &                   &                             &  & \\
   J120544.7+342252.4   & 2.068$\pm$0.0003   &   18.27            & 53498  &  2005-May-08  & SDSS             & ?                          & 53498-2089-427  & \\
          181.436164           & 2.071                        & {\bf 17.99??}  & 58538  &  2019-Feb-24   & DBSP            &  2$\times$900    &                               &  Conditions? \\
         +34.381229           &                                   &                          & 58693  &  2019-Jul-29    & DBSP            &  2$\times$1200   &                                &   \\
                                       &                                   &               &              &                           &                   &                             &  & \\
   J163852.9+282707.7   & 2.185$\pm$0.0004   &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
      249.720558407	       &  2.186$\pm$0.0007   &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
       +28.452158884        &  2.182             &                & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
                                       &                                     &                   &              &                           &                   &                             &  & \\
    J222818.7+220102.9   & 2.217$\pm$0.0021    & 19.97      & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
        337.078194              & 2.222$\pm$0.0004    &                & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
        +22.017478              &                                   &                & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
                                        &                                     &                &            &                            &                   &                              &  & \\
   \hline \hline   
  \end{tabular}
  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
Exposure times are from the {\tt plate.fits} file. 
DBSP on the Palomar 200-inch telescope is the } 
 \label{tab:obs_notes}
\end{table*}
\subsection{Spectra}
An overview of our spectroscopic observations is given in Table~\ref{tab:obs_notes}. 
The spectra are from the SDSS \citep{Stoughton2002, DR7, Schneider2010},  
the SDSS-III Baryon Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011, Dawson2013, Smee2013, Alam2015, Paris2017} 
and the SDSS-IV  Extended Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016, Abolfathi2018}. 
These quasars were targetted via a range of techniques and algorithms \citep[][]{Richards2002, Ross2012, 
Myers2015}.  
These data are supplemented by spectra from 
the Low Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I} telescope \citep{Oke1995}. 
%% The Keck Low Resolution Imaging Spectrometer", Oke, J.B., et al.. 1995, PASP, 107, 375
and the Double Spectrograph (DBSP) instrument on the Palomar {\it Hale} 5m telescope.

\subsection{Line Properties}  
We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}. \citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.} The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS. These measurements provide line profile information and N V/C IV flux ratios... 
\input{Ham17_clqs}

\subsection{Multi-wavelength properties}
We use data from the beginning of the WISE mission \citep[2010
January; ][]{Wright2010} through the fifth-year of NEOWISE-R
operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
pattern leads to coverage of the full-sky approximately once every six
months (a ``sky pass''), but the satellite was placed in hibernation
in 2011 February and then reactivated in 2013 October. Hence, our
light curves have a cadence of 6 months with a 32 month sampling gap.
%Radio ??

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  % {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
  {../plots/perObject/J1205+3422_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  {../plots/perObject/J1638+2827_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  {../plots/perObject/J2228+2201_landscape_20190920.png}
  \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
    SDSS J1205+3422 (top), 
    SDSS J1638+2827 (middle), 
    SDSS J2228+2201 (bottom). 
    % A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
  }
  \label{fig:civ_clqs}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
%%
%%
For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
standard UV/blue continuum slope increases in flux. 
the UV/blue continuum diminishes and the shape of \lya changes.

@@

In the context of CLQs at lower-$z$...  
(Balmer CLQs vs. \civ CLQs...) 
Sociis natoque penatibus et
magnis dis parturient montes, nascetur ridiculus mus. Duis tempus,
lectus nec ultricies mollis, mi orci feugiat nulla, a bibendum velit
orci nec lacus. Duis a odio in nisi egestas dictum. Nullam vel quam
mauris, eget consectetur orci. Morbi ac mi sit amet neque consectetur
tempus ac eget est. Curabitur malesuada arcu sit amet metus dictum at
dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.
